Integrated multi-omics analysis reveals Lactobacillus anti-inflammatory process in vaginal tissue

### 2021-03-19 reports/rmarkdown/manuscript/manuscript_template.Rmd
add metadata to UMAP RNAseq

image( t(top_TRX_counts[h$order,order(group_annotation[sample_use])][nrow(top_TRX_counts):1,]),
       col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
       breaks = seq(-5,5,length.out = 100),axes=F , xlab="patient groups")
points( seq(0,1,length.out = length(sample_use)),rep(par("usr")[3] - .01,length(sample_use)),
        col=pal[group_annotation[sample_use][ order(group_annotation[sample_use])]],
        pch=16,xpd=T)

points( seq(0,1,length.out = ncol(top_TRX_counts)),rep(par("usr")[3],ncol(top_TRX_counts))-.005,
        col= c("grey","red")[(!is.na(metadata$RepeatedPCR))+1][order(group_annotation[sample_use])],
        pch=16,xpd=T)
points( seq(0,1,length.out = ncol(top_TRX_counts)),rep(par("usr")[3],ncol(top_TRX_counts))-.01,
        col= c("grey","red")[as.numeric(metadata$HIVstatus)][order(group_annotation[sample_use])],
        pch=16,xpd=T)

@@

@@

>>>>

image( t(top_TRX_counts[h$order,order(group_annotation[sample_use])][nrow(top_TRX_counts):1,]),
       col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
       breaks = seq(-5,5,length.out = 100),axes=F , xlab="patient groups")
points( seq(0,1,length.out = length(sample_use)),rep(par("usr")[3] - .02,length(sample_use)),
        col=pal[group_annotation[sample_use][ order(group_annotation[sample_use])]],
        pch=16,xpd=T)

points( seq(0,1,length.out = ncol(top_TRX_counts)),rep(par("usr")[3],ncol(top_TRX_counts))-.005,
        col= c("grey","red")[(!is.na(metadata[sample_use,"RepeatedPCR"]))+1][order(group_annotation[sample_use])],
        pch=16,xpd=T)
points( seq(0,1,length.out = ncol(top_TRX_counts)),rep(par("usr")[3],ncol(top_TRX_counts))-.01,
        col= c("grey","red")[as.numeric(metadata[sample_use,"HIVstatus"])][order(group_annotation[sample_use])],
        pch=16,xpd=T)

@@

```{r, echo = FALSE, eval = TRUE,fig.asp=1}
figlabels <- letters

@@

common <- colnames(top_TRX_counts)[colnames(top_TRX_counts) %in% rownames(metadata)]

plot(UMAP_TRX,
       col=pal[metadata[common,"group_annotation"]],
       main="",xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)
empty_plot()
legend("topleft",title.adj = 0,
       legend = levels(metadata[common,"group_annotation"]),xjust = 0,yjust = 1,
       bty = "n",pch = 16,col = pal,pt.cex = 1,xpd=T)

for(i in continuous_parameters){
  xx <- metadata[common,i]
  xx[is.na(xx)] <- 0
  xx <- xx / max(xx)
  o <- order(xx)
  plot(UMAP_TRX[o,],
       col=colorRampPalette( c("grey95","navy")) (99)[ 1 + (xx[o]*98) ],
       main=i,xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)

}
```

## Figure S14

```{r, echo = FALSE, eval = TRUE,fig.asp=1}
figlabels <- letters

# g <- graph_from_adjacency_matrix(as.matrix(SNN_patients), mode = "undirected",diag = F,weighted = T)
# set.seed(1)
# l <- layout_with_fr(g,niter=3000,start.temp=30)
#

common <- colnames(top_TRX_counts)[colnames(top_TRX_counts) %in% rownames(metadata)]

mypar(6,5,mar=c(1,1,1,8))
plot(UMAP_TRX,
       col=pal[metadata[common,"group_annotation"]],
       main=i,xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)
legend(par("usr")[2],par("usr")[4],title.adj = 0,
       legend = levels(metadata[common,"group_annotation"]),xjust = 0,yjust = 1,
       bty = "n",pch = 16,col = pal,pt.cex = 1,xpd=T)

for(i in categorical_parameters){
  xx <- factor(metadata[common,i])
  plot(UMAP_TRX[,],
       col=pal[xx],
       main=i,xpd=T,
       pch=16,xlab="",ylab="",frame=F,axes=F,font.main=1,cex.main=1)
legend(par("usr")[2],par("usr")[4],title.adj = 0,
       legend = levels(xx),xjust = 0,yjust = 1,
       bty = "n",pch = 16,col = pal,pt.cex = 1,xpd=T)
}
```

## Figure S15
